### 2017-07-06 lafaySimulatedScenePerception.tex
fixing references

The remaining of the paper is organized as follows: the soundscape simulator \emph{simScene} is introduced in Section \ref{sec:simulator}. The three experiments,  1.a \emph{simulation}, 1.b \emph{pleasantness evaluation}, and 2 \emph{pleasantness evaluation after modification of the scenes} are respectively presented in Sections \ref{sec:simulation}, \ref{sec:evaluation}, and \ref{sec:modification}. Conclusions and discussion about future work follow in Section \ref{sec:conclusion}. Experiment 1.a is based on a pilot study described in \cite{lafay2014new}.

@@

\section{The simulator}
\label{sec:simscene}

@@

\section{Expérience 1}
\label{sec:xp1}

\subsection{Objectif}

@@

Experiment 1 aims at using the simulation paradigm to investigate the specific influences of the various sound sources constituting urban soundscapes on the perceived pleasantness. For that, two first experiments are planned (\cf~Figure~\ref{fig:xp1_2}):
\begin{itemize}
\item \emph{experiment 1.a (simulation)}: during this experiment, participants have to create urban sound environments, using the simulation tool \emph{Simscene}, see Section~\ref{sec:simscene}. Each of them creates two environments: one ideal / pleasant and the other one, non ideal / unpleasant.
\item \emph{experiment 2.a (evaluation)}: actually, after the simulation phase, we only have a binary information on the emotional properties of the respective scenes: ideal (i) and non ideal (ni). This second experimental step aims at investigating our knowledge on pleasantness. For that, a second group of participants are asked to evaluate the pleasantness of each simulated scene, on a semantic scale. This evaluation protocol has two goals:
\begin{enumerate}
\item to evaluate the respective influence on the pleasantness of the various sources composing the scenes (i or ni)
\item to detect the presence of \emph{outliers} or ambiguous samples. For the remainder of the study, the defined hedonic properties (i and ni) are used as ground truth. Then, we must have to be sure that no ambiguity exists between extreme cases of i and ni scenes; i.e that the lower i-scene is really above the upper ni-scene,  in terms of pleasantness rating.
\end{enumerate}
\end{itemize}

@@

\begin{table}[t]
\centering
\begin{tabular}{c c}
Termes                         & Acronyms              \\
\hline
Niveau                         & $L$                    \\
Niveau (événements)            & $L(E)$                 \\
Niveau (textures)              & $L(T)$                 \\
Agrément moyen (par scène)     & $\mathcal{A}_{scene}$  \\
Agrément moyen (par sujet)     & $\mathcal{A}_{sujet}$  \\
                               &                        \\
idéale/agréable                & i                      \\
non-idéale/désagréable         & ni                     \\
scène idéale/agréable          & i-scene                \\
scène non-idéale/désagréable   & ni-scene               \\
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Acronyme des variables utilisées dans le cadre des expériences sensorielles.}
\label{tab:acronyme}
\end{table}

@@

Finally, it appears that the $p@5$ obtained with $E_m$ is equal – or above – to the ones obtained with $E$ or $ET$, although a partial information is used in that case to describe the scenes. The dimension of the vectors $S$ for $E_m$ is lower than the dimension of vector $S$ for $E$, itself lower than the dimension of vector S obtained when all the classes are considered ($ET$). Moreover, in the case when the sound markers are not taken into account for the description ($E_{w/o,m}$), the results fall even going under those obtained with only the textures. This confirms that most of the semantic information allowing to differentiate between i- and ni- scenes is included in the markers.

@@

\begin{enumerate}
\item contrairement à ce que nous avions constaté avec les descripteurs structurels, une description sémantique de la composition des scènes, en terme de présence/absence de sources sonores, permet de bien distinguer les deux types d'environnement (i ou ni);
\item l'information sémantique est majoritairement portée par les classes d'événements sonores;
\item parmi les classes d'événements, seule une partie, \ie~les marqueurs sonores, est nécessaire pour faire la distinction entre les i- et ni-scènes.
\end{enumerate}

@@

\section{Experiment 2: modification of the semantic content}
\label{sec:xp3}

@@

\section{Outcomes for sounscape perception}

%Les expériences ont montré que la majorité des descripteurs utilisés, qu'ils soient sémantiques ou structurels, permettent de faire la distinction entre une scène idéale et une scène non-idéale.

@@

\appendix
\section{Taxonomies des classes de sons}
\label{app:taxonomie}

@@

\newpage
\section{Dispersions des notes données par les sujets lors de l'expérience 2}
\label{app:xp2}

>>>>

The remaining of the paper is organized as follows: the soundscape simulator \emph{simScene} is introduced in Section \ref{sec:simulator}. The experiments  1.a \emph{simulation} and  1.b \emph{pleasantness evaluation} are presented in Section \ref{sec:simulation}. Experiment 2 \emph{pleasantness evaluation after modification of the scenes} is presented in Section \ref{sec:modification}. Conclusions and discussion about future work follow in Section \ref{sec:conclusion}. Experiment 1.a is based on a pilot study described in \cite{lafay2014new}.

@@

\section{The simulator}
\label{sec:simulator}

@@

\section{Experiment 1}
\label{sec:simulation}

@@

Experiment 1 aims at using the simulation paradigm to investigate the specific influences of the various sound sources constituting urban soundscapes on the perceived pleasantness. For that, two first experiments are planned (\cf~Figure~\ref{fig:xp1_2}):
\begin{itemize}
\item \emph{experiment 1.a (simulation)}: during this experiment, participants have to create urban sound environments, using the simulation tool \emph{Simscene}, see Section~\ref{sec:simulator}. Each of them creates two environments: one ideal / pleasant and the other one, non ideal / unpleasant.
\item \emph{experiment 2.a (evaluation)}: actually, after the simulation phase, we only have a binary information on the emotional properties of the respective scenes: ideal (i) and non ideal (ni). This second experimental step aims at investigating our knowledge on pleasantness. For that, a second group of participants are asked to evaluate the pleasantness of each simulated scene, on a semantic scale. This evaluation protocol has two goals:
\begin{enumerate}
\item to evaluate the respective influence on the pleasantness of the various sources composing the scenes (i or ni)
\item to detect the presence of \emph{outliers} or ambiguous samples. For the remainder of the study, the defined hedonic properties (i and ni) are used as ground truth. Then, we must have to be sure that no ambiguity exists between extreme cases of i and ni scenes; i.e that the lower i-scene is really above the upper ni-scene,  in terms of pleasantness rating.
\end{enumerate}
\end{itemize}

@@

\begin{table}[t]
\centering
\begin{tabular}{c c}
Terms                         & Acronyms              \\
\hline
Level                        & $L$                    \\
Level (events)            & $L(E)$                 \\
Level (textures)              & $L(T)$                 \\
Average pleasantness (per scene)     & $\mathcal{A}_{scene}$  \\
Average pleasantness (per subject)     & $\mathcal{A}_{sujet}$  \\
                               &                        \\
ideal/pleasant                & i                      \\
non-ideal/unpleasant         & ni                     \\
scene ideal/pleasant          & i-scene                \\
scene non-ideal/unpleasant   & ni-scene               \\
\hline
\end{tabular}
\vspace{0.5mm}
\caption{Acronyms of features used in the analysis of the sensory experiments.}
\label{tab:acronyme}
\end{table}

@@

Lastly, it appears that the $p@5$ obtained with $E_m$ is equal – or above – to the ones obtained with $E$ or $ET$, although a partial information is used in that case to describe the scenes. The dimension of the vectors $S$ for $E_m$ is lower than the dimension of vector $S$ for $E$, itself lower than the dimension of vector S obtained when all the classes are considered ($ET$). Moreover, in the case when the sound markers are not taken into account for the description ($E_{w/o,m}$), the results fall even going under those obtained with only the textures. This confirms that most of the semantic information allowing to differentiate between i- and ni- scenes is included in the markers.

@@

\begin{enumerate}
\item unlike what we outlined with the structural features, a semantic description of the scenes constitution in terms of presence / absence of sound sources, allows to differentiate the two types of environments (i or ni);
\item the semantic information is mainly contained in the event sound classes;
\item only a part of the event classes, i.e. the sound markers, are useful to differentiate the i- and ni- scenes.
\end{enumerate}

@@

\section{Experiment 2: modification of the semantic content}
\label{sec:modification}

@@

\section{Outcomes for soundscape perception}
\label{sec:conclusion}
%Les expériences ont montré que la majorité des descripteurs utilisés, qu'ils soient sémantiques ou structurels, permettent de faire la distinction entre une scène idéale et une scène non-idéale.

@@

\appendix
\section{Taxonomy of sound classes}
\label{app:taxonomie}

@@

\newpage
\section{Distribution of scores given par the subjects during experiment 2}
\label{app:xp2}
